COMMENTS FOR THE AUTHOR:

Whenever possible, please add relevant references from The Visual Computer. It is important to cite related work from the journal you are publishing in.


Reviewer #1: 
-  The literature review is not sufficient. more literature review is needed,
% [Andrea], aggiungere da COMPAG e cercare da Visual Computer
-  The writing and presentation of the paper have some issues. Please clear the paper.
% [Andrea]
-To give better insights to the reader other approaches can be added. Following references can be useful for the same.
Linear discriminant multi-set canonical correlations analysis (LDMCCA): an efficient approach for feature fusion of finger biometrics
Saliency detection based on integrated features
IoT Security Based on Iris Verification Using Multi-Algorithm Feature Level Fusion Scheme
% [Andrea] aggiungere una parte nel SOTA in cui parliamo della fusione delle feature e citiamo questi tre lavori
- The references are up to date but some are not in the right format.
% [Andrea]
- Conclusion section is poor, please improve.
% [Cecilia]
- The conclusions section should conclude that you have achieved from the study, contributions of the study to academics and practices. In addition, list the advantages and disadvantages of the proposed solution, as well as indicate the limitations of work. Further, mention the recommendations of future works.
% [Cecilia] inserire lista di contributi nell'intro e riprenderli nelle conclusioni
- Compare your results with the imp methods published in the litertaure
% [Cecilia] - aggiungere comparazione con COMPAG
% - motivare maggiormente che il plugin è utilizzabile da non experts


Reviewer #4: 
1. There are some layout problems in this paper. For example, the format of section title and text is same in Abstract, and the table title of Table 4 is under the table.

2.      Some descriptions are redundant in this paper. For example, Introduction should be segmented for clarity.

3.      This paper lacks of visualization results in experimental results.
4.      And there is also lacking of comparison experiments with CNN-based methods to prove the effectiveness of the proposed tool.

5.      For the references, please add more references published in recent years

